Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Density parameter modifications

  rbind.fill(
    data.frame(
      xvar = names(data)[ycol], 
      yvar = names(data)[xcol],
      x = data[, xcol], 
      y = data[, ycol], 
      points = T,
      data
    ),
    data.frame(
      yvar = names(data)[ycol], 
      xvar = names(data)[xcol],
      x = mean(range(data[, ycol])), 
      y = mean(range(data[, xcol])),
      label = round(cor(data[,xcol], data[,ycol]), 3),
      points = F
    )
  )
}))
all$xvar <- factor(all$xvar, levels=names(data))
all$yvar <- factor(all$yvar, levels=names(data))
densities <- do.call("rbind", lapply(1:ncol(data), function(i) {
    tmp <- density(data[,i])
    data.frame(
      xvar = names(data)[i], 
      yvar = names(data)[i],
      x = tmp$x, 
      y = tmp$y/max(tmp$y)* diff(range(tmp$x)) + min(tmp$x)
    )
  }))

>>>>

  rbind.fill(
    data.frame(
      xvar = names(data)[ycol], 
      yvar = names(data)[xcol],
      x = data[, xcol], 
      y = data[, ycol], 
      points = T,
      data
    ),
    data.frame(
      yvar = names(data)[ycol], 
      xvar = names(data)[xcol],
      x = mean(range(data[, ycol])), 
      y = mean(range(data[, xcol])),
      label = round(cor(data[,xcol], data[,ycol]), 3),
      points = F
    )
  )
}))
all$xvar <- factor(all$xvar, levels=names(data))
all$yvar <- factor(all$yvar, levels=names(data))
densities <- do.call("rbind", lapply(1:ncol(data), function(i) {
    tmp <- density(data[,i], cut = 1, adjust=.75)
    data.frame(
      xvar = names(data)[i], 
      yvar = names(data)[i],
      x = tmp$x, 
      y = tmp$y/max(tmp$y)* diff(range(tmp$x)) + min(tmp$x)
    )
  }))
